The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-12 paper/ms.tex
small changes

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 64~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 64 of these stars as clearly evolved systems, and the remaining~38 lie apparently on the main sequence.

@@

Among the~64 red giants identified in this sample, for~30 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:

>>>>

% Abstract of the paper
\begin{abstract}
Here we present the first data release of the \kepler Smear Campaign, using collateral `smear' data obtained by \kepler to reconstruct light curves of 102~stars too bright to have been otherwise targeted. We describe the pipeline developed to extract and calibrate these light curves, and show that we attain photometric precision comparable to stars analyzed by the standard pipeline in the nominal \kepler mission. In this Paper, we focus in particular on a subset of these consisting of 66~red giants for which we detect solar-like oscillations. Using high-resolution spectroscopy from the Tillinghast Reflector \'{E}chelle Spectrograph (TRES) together with asteroseismic modelling, we obtain the stellar densities and derive masses, radii and ages of~34 of these red giant and red clump stars as benchmarks. All source code, light curves, TRES spectra, and asteroseismic and stellar parameters are publicly available as a \kepler legacy sample.
\end{abstract}

@@

We identify the evolutionary state of stars in the main sequence versus evolved stars first from the \gaia colour-magnitude diagram in Figure~\ref{hrdiagram}. Taking a cutoff in \gaia $Bp-Rp > 1$, we identify 66 of these stars as evolved systems, and the remaining~36 lie apparently on the main sequence.

@@

Among the~66 red giants identified in this sample, for~32 the timescale of their variability is of the same order as a \kepler quarter and they are thus badly affected by systematics and systematics correction. In Table~\ref{all_stars} we have noted these as `long-period variables' (LPVs), without specifically meaning these are LPVs by a particular astrophysical definition, and they are discussed further in Section~\ref{lpvs}. For the~34 giants for which there is high-SNR shorter-timescale variability, we have attempted to extract the asteroseismic parameters \numax and $\langle \Dnu \rangle$ \citep{KB95,2013ARA&A..51..353C}. These constrain fundamental stellar parameters through the approximate scaling relations:
